MINOS Handover Plots

### 2024-05-31 minos/validation/handovers.Rmd
changing hanvoers to use imputed data. adding in script to get all ukhls data.

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
